### 2014-04-15 report/paper.tex
added report

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

%\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{graphicx} % for pdf, bitmapped graphics files
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
%\usepackage{algorithm,algpseudocode}

%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{enumerate}

\title{\LARGE \bf
Stereo Matching using Graphcut-based Optimization}

\author{Seyed Abbas Sadat\\
Simon Fraser University\\
sas21@sfu.ca% <-this % stops a space
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\end{abstract}

\section{INTRODUCTION}

\bibliographystyle{ieeetr} 
\bibliography{refs}

\end{document}

### 2014-04-15 src/GraphcutStereo.cpp

@@ -167,6 +167,7 @@ void GraphcutStereo::Update()
     bool flag = drawHighRes;
     if(alpha_beta_swap)
         drawHighRes = AlphaBetaSwap(((double)(currentF%(nF)))*0.5, ((double)(currentF/(nF)))*0.5);
+        //drawHighRes = AlphaBetaSwap(((double)(currentF%(nF))), ((double)(currentF/(nF))));
     else
         drawHighRes = AlphaExpansion(currentF);
 
@@ -362,13 +363,20 @@ double GraphcutStereo::V(int i1, int j1, double dp1, int i2, int j2, double dp2)
 
     double val = 0;
     if(alpha_beta_swap)
-        val = 50*fabs(dp1-dp2); //alpha beta swap
-    else
-        val = 5*fabs(dp1-dp2); //alpha expansion
-
-    if(val >= 50)
     {
-        val = 50;
+        val = 200*fabs(dp1-dp2); //alpha beta swap
+        if(val >= 100)
+        {
+            val = 100;
+        }
+    }
+    else
+    {
+        val = 5*fabs(dp1-dp2); //alpha expansion
+        if(val >= 50)
+        {
+            val = 50;
+        }
     }
 
     return val;
@@ -437,7 +445,7 @@ bool GraphcutStereo::AlphaBetaSwap(double f1, double f2)
 {
     static int round = 0;
     round++;
-    if(round > nF*nF*4)
+    if(round > nF*nF*2)
     {
         Display();
         exit(0);
@@ -635,7 +643,7 @@ bool GraphcutStereo::AlphaBetaSwap(double f1, double f2)
         if( newE < lastE)
         {
            //round = 0;
-           printf("flow reduced from:%f to:%f Time:%f\n", lastE, newE,elapsedTime2/1000.0);
+           printf("DTime:%f %%%.1f\n", elapsedTime2/1000.0, 100*round/(nF*nF*2.0f));
             lastE = newE;
             disparity.copy_from(newdisp);
             disparity4x4 = CVD::halfSample(disparity);

### 2014-04-15 report/paper.tex
report

@@
 
-\title{\LARGE \bf
+\title{Project Report:\\\LARGE \bf
 Stereo Matching using Graphcut-based Optimization}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-\end{abstract}
 
@@
 
+\begin{figure*}[t]
+        \centering
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l4.png}
+                \caption{"Art" Color image}
+                \label{fig:trees}
+        \end{subfigure}%
+                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/disp4.png}
+                \caption{Ground Truth}
+                \label{fig:farm}
+        \end{subfigure}
+                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l4disparity-expansion.png}
+                \caption{$\alpha$-expansion}
+                \label{fig:farm}
+        \end{subfigure}
+                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l4disparity-swap.png}
+                \caption{$\alpha\beta$-swap}
+                \label{fig:farm}
+        \end{subfigure}
+                        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l4disparity-expansion-sub.png}
+                \caption{$\alpha$-expansion - subpixel accuracy}
+                \label{fig:farm}
+        \end{subfigure}
+                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l4disparity-swap-sub.png}
+                \caption{$\alpha\beta$-swap - subpixel accuracy}
+                \label{fig:farm}
+        \end{subfigure}
+        \caption{Disparity image for the "Art" dataset using the both $\alpha\beta$-swap and $\alpha$-expansion with pixel and subpixel accuracies.}
+        \label{fig:realmaps}
+\end{figure*}
+
+\begin{figure*}[t]
+        \centering
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l2.png}
+                \caption{"Wood1" Color image}
+                \label{fig:trees}
+        \end{subfigure}%
+                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/disp2.png}
+                \caption{Ground Truth}
+                \label{fig:farm}
+        \end{subfigure}
+                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l2disparity-expansion.png}
+                \caption{$\alpha$-expansion}
+                \label{fig:farm}
+        \end{subfigure}
+                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l2disparity-swap.png}
+                \caption{$\alpha\beta$-swap}
+                \label{fig:farm}
+        \end{subfigure}
+                        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l2disparity-expansion-sub.png}
+                \caption{$\alpha$-expansion - subpixel accuracy}
+                \label{fig:farm}
+        \end{subfigure}
+                ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l2disparity-swap-sub.png}
+                \caption{$\alpha\beta$-swap - subpixel accuracy}
+                \label{fig:farm}
+        \end{subfigure}
+        \caption{Disparity image for the "Wood1" dataset using the both $\alpha\beta$-swap and $\alpha$-expansion with pixel and subpixel accuracies.}
+        \label{fig:realmaps}
+\end{figure*}
+
+In this project we developed a stereo matching system based on graph-cut optimization framework \cite{boykov2001fast}.
+In stereo matching problem, 2 images taken from 2 cameras that are in the same hozirontal like The input to the system is a pare of images
+
+\section{Graphcut-based Optimization}
+\section{Stereo Matching}
+\section{Experiments and Results}
 \bibliographystyle{ieeetr} 

### 2014-04-15 src/GraphcutStereo.cpp

@@ -13,8 +13,14 @@ GraphcutStereo::GraphcutStereo(int argc, char **argv)
     else
         alpha_beta_swap = false;
 
+    subpixel = false;
+
     drawHighRes = false;
-    nF = 40;
+    if(subpixel)
+        nF = 40;
+    else
+        nF = 20;
+
     fname.clear();
     fname.append(argv[1]);
 
@@ -166,8 +172,12 @@ void GraphcutStereo::Update()
 
     bool flag = drawHighRes;
     if(alpha_beta_swap)
-        drawHighRes = AlphaBetaSwap(((double)(currentF%(nF)))*0.5, ((double)(currentF/(nF)))*0.5);
-        //drawHighRes = AlphaBetaSwap(((double)(currentF%(nF))), ((double)(currentF/(nF))));
+    {
+        if(subpixel)
+            drawHighRes = AlphaBetaSwap(((double)(currentF%(nF)))*0.5, ((double)(currentF/(nF)))*0.5);
+        else
+            drawHighRes = AlphaBetaSwap(((currentF%(nF))), (currentF/(nF)));
+    }
     else
         drawHighRes = AlphaExpansion(currentF);
 
@@ -211,8 +221,8 @@ void GraphcutStereo::glDraw()
     ImageRef size = disparity4x4.size();
     glPointSize(5);
     glBegin(GL_QUADS);
-    for(int i=0; i<size.y-ds; i+=ds)
-        for(int j=0; j<size.x-ds; j+=ds)
+    for(int i=1; i<size.y-ds; i+=ds)
+        for(int j=1; j<size.x-ds; j+=ds)
         {
 	    
 
@@ -277,7 +287,7 @@ double GraphcutStereo::D(int i, int j, double dp)
 
     double val=0;
     int w=1;
-    for(int ii=i; ii<i+1;ii++)
+    for(int ii=i-w; ii<=i+w;ii++)
         for(int jj=j-w; jj<=j+w;jj++)
         {
             int pixVal = 0;
@@ -306,7 +316,7 @@ double GraphcutStereo::D(int i, int j, double dp)
             val+=pixVal;
         }
 
-    double n = 3;
+    double n = 9;
     val = (val/(n))<200?(val/(n)):200;
 
     return val*val;
@@ -364,7 +374,7 @@ double GraphcutStereo::V(int i1, int j1, double dp1, int i2, int j2, double dp2)
     double val = 0;
     if(alpha_beta_swap)
     {
[…]

### 2014-04-15 src/GraphcutStereo.h

@@ -57,6 +57,7 @@ private:
     CVD::ImageRef imgSize;
 
     bool alpha_beta_swap;
+    bool subpixel;
 
     //subsamplings
     CVD::Image<float> disparity4x4;

### 2014-04-16 report/paper.tex
report

@@
 In this project we developed a stereo matching system based on graph-cut optimization framework \cite{boykov2001fast}.
-In stereo matching problem, 2 images taken from 2 cameras that are in the same hozirontal like The input to the system is a pare of images
+In stereo matching problem, 2 images taken from 2 cameras that are on the same horizontal line are to be matched pixel by pixel.
+Therefore, for each pixel on the left image, we should find its corresponding pixel on the right image.
+According to the assumptions, we know that if $(i,j)$ is the coordinate of the pixel in the left image, the coordinate of the corresponding pixel in the right image will be $(i,j-d)$.
+The unknown variable $d$ is called disparity and is defined in the image space.
+Disparity is inversely proportional to the depth of the pixel, i.e., the higher the disparity the closer the object.
+The disparity is not always observable using only 2 images because part of the scene can be occluded in either of the left or right images and hence no matched pixel can be found.
+
+The stereo matching problem is formulated as: given a left and right image, find the most probable disparity image.
+This $maximum a posteriori$ problem is often solved by finding a disparity image that minimizes some energy function.
+The energy function includes some terms that promote data fidelity (data terms) as well as other terms that support prior assumptions about the solution, e.g., smoothness (smoothness term).
+These energy functions are non-convex and finding a global optimum it very difficult.
+Instead, approaches that result in approximation solutions are preferred.
+One way to reach a local optimum in the minimization is to perform gradient descent.
+Graph-cuts offer a framework that enables us to generate a movement (step) of current solution that is steepest in terms of minimizing the energy function.
+By generating and performing these steps iteratively, we reach a local optimum.
+
+In section \ref{graphcut} we briefly explain how to generate gradient descent moves for a general pixel labelling problem.
 
 \section{Graphcut-based Optimization}
+\label{graphcut}
+The energy function that we use for stereo matching has the following form:
+\begin{figure}[h]
+                \centering
+                \includegraphics[width=0.35\textwidth]{imgs/energy.png}
+                \label{fig:farm}
+\end{figure}
+
 \section{Stereo Matching}

### 2014-04-16 report/paper.tex
report

@@
 
+In this project we developed a stereo matching system based on graph-cut optimization framework \cite{boykov2001fast}.
+In stereo matching problem, 2 images taken from 2 cameras that are on the same horizontal line are to be matched pixel by pixel.
+Therefore, for each pixel on the left image, we should find its corresponding pixel on the right image.
+According to the assumptions, we know that if $(i,j)$ is the coordinate of the pixel in the left image, the coordinate of the corresponding pixel in the right image will be $(i,j-d)$.
+The unknown variable $d$ is called disparity and is defined in the image space.
+Disparity is inversely proportional to the depth of the pixel, i.e., the higher the disparity the closer the object.
+The disparity is not always observable using only 2 images because part of the scene can be occluded in either of the left or right images and hence no matched pixel can be found.
+
+The stereo matching problem is formulated as: given a left and right image, find the most probable disparity image.
+This \emph{maximum a posteriori} problem is often solved by finding a disparity image that minimizes some energy function.
+The energy function includes some terms that promote data fidelity (data terms) as well as other terms that support prior assumptions about the solution, e.g., smoothness (smoothness term).
+These energy functions are non-convex and finding a global optimum it very difficult.
+Instead, approaches that result in approximation solutions are preferred.
+One way to reach a local optimum in the minimization is to perform gradient descent.
+Graph-cuts offer a framework that enables us to generate a movement (step) of current solution that is steepest in terms of minimizing the energy function.
+By generating and performing these steps iteratively, we reach a local optimum.
+
+In section \ref{graphcut} we briefly explain how to generate gradient descent moves for a general pixel labelling problem.
+
+\section{Graphcut-based Optimization}
+\label{graphcut}
+The energy function that we use for stereo matching has the following form:
+\begin{figure}[h]
+                \centering
+                \includegraphics[width=0.35\textwidth]{imgs/energy.png}
+                \label{fig:farm}
+\end{figure}
+
+Here $D_p(f_p)$ is the data term, i.e.
+cost of assigning label $f_p$ to pixel $p$.
+This cost is calculated based on the input data (left and right images in stereo matching).
+The $V_{p,q}(f_p,f_q)$ term is the pairwise cost of two neighbours $p$, $q$ having labels $f_p$, $f_q$ respectively.
+
+Assuming that we are at some arbitrary solution we generate an $\alpha\beta-swap$ move or $\alpha-expansion$ move.
+Next, if performing the new move reduces the energy function, we apply the move on the current solution and generate a new move again iteratively.
+
+For computing the best move at each solution, i.e.
+a move with the largest reduction of energy function, we construct a graph network based on the current solution and the input images.
+The weights of the edges are carefully defined so that the cost of any $cut$ in the created graph equals the cost of the specific move in the labelling problem (plus a constant).
+Therefore if we find the minimum cut of the graph, we can convert it to a move that reduces the energy function the most.
+The following sections describe $\alpha\beta-swap$ and $\alpha-expansion$ moves.
+
+\begin{figure}[h]
+                \centering
+                \includegraphics[width=0.5\textwidth]{imgs/swap.png}
+                \caption{The graph corresponding to a $\alpha\beta-swap$.}
+                \label{abswap}
+\end{figure}
+
+\subsection{$\alpha\beta-swap$} 
+In $\alpha\beta-swap$ move, subset of the pixel having label $\alpha$ can be changed to label $\beta$ and vice versa.
+Therefore only the union of the pixel with $\alpha$ or $\beta$ will change labels and other pixel remain the same.
+Therefore in each cycle of the algorithm this move is computed for each possible label pair and then is applied on the current solution if it reduces the energy function.
+In order to find the best possible label change in an $\alpha\beta-swap$, the minimum graph-cut problem shown in figure \ref{abswap} is solved:
+
+The terminals are the labels $\alpha$ and $\beta$ and the middle nodes are all the pixels with either $\alpha$ or $\beta$ label.
+The weight of the terminal edges are the data terms $D_p(\alpha)$ or $D_p(\beta)$, i.e.
+the cost of assigning the terminal label to the pixel.
+The weight of the edges between middle nodes are the pairwise smoothness term $V_{p,q}(\alpha,\beta)$.
+Please see \cite{boykov2001fast} for details.
+
+\subsection{$\alpha-expansion$}
+In $\alpha-expansion$ move, a subset of the pixel that do not have label $\alpha$ can be changed to label $\alpha$ and labels of the rest of the pixels remain unchanged.
+Therefore in each cycle of the algorithm this move is computed for each possible label and then is applied on the current solution if it reduces the energy function.
+In order to find the best possible label change in an $\alpha-expansion$, the minimum graph-cut problem shown in figure \ref{aexpansion} is solved:
+
+\begin{figure}[h]
+                \centering
+                \includegraphics[width=0.5\textwidth]{imgs/expansion.png}
+                \caption{The graph corresponding to a $\alpha-expansion$.}
+                \label{aexpansion}
+\end{figure}
+
+The terminals are the labels $\alpha$ and $\overline{\alpha}$.
+Selecting $\overline{\alpha}$ simply means that the pixel will keep its current label.
+The middle nodes are all the pixels with labels other than $\alpha$.
+The weight of the terminal edges are the data terms $D_p(\alpha)$ or $D_p(f_p)$, i.e.
+the cost of assigning the terminal label to the pixel.
+Notice that $D_p(f_p)$ is used when $\overline{\alpha}$ is selected for pixel $p$ and $f_p$ is the current label of pixel $p$.
+The weight of the edges between middle nodes that with the same labels are the pairwise smoothness term $V_{p,q}(\alpha,f_p)$ in which $f_p$ is the current label of the pair pixels.
+If the labels of the two neighbour pixels are different we add another axillary node with edges to both corresponding neighbour nodes with weights $V(\alpha,f_p)$ and $V(f_p, \alpha)$ and an edge to the terminal $\overline{\alpha}$ with weight $V(f_q,f_p)$.
+Please see \cite{boykov2001fast} for details.
+
+\section{Stereo Matching}
+\section{Experiments and Results}
 \begin{figure*}[t]
@@
 
-In this project we developed a stereo matching system based on graph-cut optimization framework \cite{boykov2001fast}.
-In stereo matching problem, 2 images taken from 2 cameras that are on the same horizontal line are to be matched pixel by pixel.
-Therefore, for each pixel on the left image, we should find its corresponding pixel on the right image.
-According to the assumptions, we know that if $(i,j)$ is the coordinate of the pixel in the left image, the coordinate of the corresponding pixel in the right image will be $(i,j-d)$.
-The unknown variable $d$ is called disparity and is defined in the image space.
-Disparity is inversely proportional to the depth of the pixel, i.e., the higher the disparity the closer the object.
-The disparity is not always observable using only 2 images because part of the scene can be occluded in either of the left or right images and hence no matched pixel can be found.
-
-The stereo matching problem is formulated as: given a left and right image, find the most probable disparity image.
-This $maximum a posteriori$ problem is often solved by finding a disparity image that minimizes some energy function.
-The energy function includes some terms that promote data fidelity (data terms) as well as other terms that support prior assumptions about the solution, e.g., smoothness (smoothness term).
-These energy functions are non-convex and finding a global optimum it very difficult.
-Instead, approaches that result in approximation solutions are preferred.
-One way to reach a local optimum in the minimization is to perform gradient descent.
-Graph-cuts offer a framework that enables us to generate a movement (step) of current solution that is steepest in terms of minimizing the energy function.
-By generating and performing these steps iteratively, we reach a local optimum.
-
-In section \ref{graphcut} we briefly explain how to generate gradient descent moves for a general pixel labelling problem.
-
-\section{Graphcut-based Optimization}
-\label{graphcut}
-The energy function that we use for stereo matching has the following form:
-\begin{figure}[h]
-                \centering
-                \includegraphics[width=0.35\textwidth]{imgs/energy.png}
-                \label{fig:farm}
-\end{figure}
-
-\section{Stereo Matching}
-\section{Experiments and Results}
 \bibliographystyle{ieeetr} 

### 2014-04-16 report/paper.tex
report

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\emph{Note: All the figures should be seen on screen in order to distinguish the gray level changes. Also for pixel coordinates $(i,j)$ means row $i$ and column $j$.}
 
@@
 \section{Stereo Matching}
+As mentioned earlier in stereo matching we want to find the most probable disparity image given the left and right input images.
+Therefore we minimize an energy function with data terms and smoothness terms involving the disparity labels.
+More specifically for data term we use the following:
+\begin{center}
+$D_{i,j}(f)$ $=$ $min\{|I(i,j)-I'(i,j-f)|,200\}$
+\end{center}
+where $I$ and $I'$ are the left and right image respectively and $f$ is the proposed disparity for pixel $(i,j)$.
+The constant (200) is to make sure that we are robust to noisy data and outliers.
+In addition to single pixel cost, we also use window based cost which is the mean of the above data term in a window of size $w$ centred around the corresponding pixel.
+We will discuss the results in section \ref{exper}.
+
+For the smoothness term we use 2 different models. The first one is the Potts model as follow:
+\begin{center}
+$V_{p,q}(f_p,f_q)$ $=$ $50*T(f_p \neq f_q)$
+\end{center}
+This means that if two neighbouring pixel are assigned different disparities, 50 units will be added to the energy function.
+This model tend to generate large segments with same disparity and is not appropriate for scenes that there is a gradient in depth.
+We show this in the experiments.
+For a better smoothness function which preserves linear depth changes we use the following smoothness term:
+\begin{center}
+$V_{p,q}(f_p,f_q)$ $=$ $min\{5*|f_p - f_q|,50\}$
+\end{center}
+This smoothness term penalizes linearly as a function of the disparity difference.
+We need to cut off these penalties at some point to preserve the edges.
+We will discuss the results in the next section.
 \section{Experiments and Results}
+\label{exper}
+For the experiments we used the publicly available Middlebury stereo dataset\footnote{http://vision.middlebury.edu/stereo/data/}.
+Here, we only present the results for 2 different images "Art" in Fig.
+\ref{art} and "Wood1" in Fig.
+\ref{wood1}.
+These figures show the result for pixel level accuracy and subpixel accuracy.
+By subpixel accuracy we mean that the disparity could have 0.5 disparities.
+Therfore we can see that the gray level can be different very slightly from the results with pixel level accuracy because of finer resolution.
+
+Next we examine the effect of smoothness model in the energy function.
+The results are shown in Figure \ref{models}.
+It can be seen that the Potts model does not allow smooth changes in disparity and large areas with single disparity is preferred.
+On the other hand, with linear model, a number of disparity changes can be recognized which results in a little smoother disparity image.
+
+We also tested the effect of the size of the window that is used to aggregate the data term.
+Figure \ref{window} demonstrate the results for 3 different window sizes.
+We can see that as the window size grows, the changes in disparity becomes smoother.
+This window act like a low pass filter that removes the high frequencies in the disparity image.
+
+For implementation of this project we used the following libraries:
+\begin{itemize}
+\item Opencv\footnote{http://opencv.org}
+\item Min-cut library\footnote{http://vision.csd.uwo.ca/code/}
+\end{itemize}
+The source code of this project is also publicly available at: $https://github.com/asadat/graphcut\_stereo$.
+
+\begin{figure}
+        \centering
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l2disparity-expansion-potts.png}
+                \caption{The Potts model}
+                \label{fig:trees}
+        \end{subfigure}%
+
+                 %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l2disparity-expansion-linear.png}
+                \caption{Linear model}
+                \label{fig:farm}
+        \end{subfigure}
+        \caption{Disparity image for the "Wood1" dataset using $\alpha$-expansion with Potts and linear smoothness models.}
+        \label{models}
+\end{figure}
+
+\begin{figure}[t]
+        \centering
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l4disparity-expansion-w1.png}
+                \caption{$w=1$}
+                \label{fig:trees}
+        \end{subfigure}%
+
+                 %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l4disparity-expansion-w3.png}
+                \caption{$w=3$}
+                \label{fig:farm}
+        \end{subfigure}
+
+                         %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}[b]{0.3\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{imgs/l4disparity-expansion-w5.png}
+                \caption{$w = 5$}
+                \label{fig:farm}
+        \end{subfigure}
+        \caption{Disparity image for the "Art" dataset using $\alpha$-expansion with 3 different window sizes for data term aggregation.}
+        \label{window}
+\end{figure}
+
 \begin{figure*}[t]
@@
         \caption{Disparity image for the "Art" dataset using the both $\alpha\beta$-swap and $\alpha$-expansion with pixel and subpixel accuracies.}
-        \label{fig:realmaps}
+        \label{art}
 \end{figure*}
@@
         \caption{Disparity image for the "Wood1" dataset using the both $\alpha\beta$-swap and $\alpha$-expansion with pixel and subpixel accuracies.}
-        \label{fig:realmaps}
+        \label{wood1}
 \end{figure*}

### 2014-04-16 src/GraphcutStereo.cpp

@@ -287,8 +287,8 @@ double GraphcutStereo::D(int i, int j, double dp)
 
     double val=0;
     int w=1;
-    for(int ii=i-w; ii<=i+w;ii++)
-        for(int jj=j-w; jj<=j+w;jj++)
+    for(int ii=i-w; ii<i+w+1;ii++)
+        for(int jj=j-w; jj<j+w+1;jj++)
         {
             int pixVal = 0;
             int jj2 = jj-dp;
@@ -316,7 +316,7 @@ double GraphcutStereo::D(int i, int j, double dp)
             val+=pixVal;
         }
 
-    double n = 9;
+    double n = (2*w+1)*(2*w+1);
     val = (val/(n))<200?(val/(n)):200;
 
     return val*val;
@@ -382,7 +382,7 @@ double GraphcutStereo::V(int i1, int j1, double dp1, int i2, int j2, double dp2)
     }
     else
     {
-        val = 50*fabs(dp1-dp2); //alpha expansion
+        val = 5*fabs(dp1-dp2); //alpha expansion
         if(val >= 50)
         {
             val = 50;

### 2014-04-16 UI/bin/moc_mainwindow.cpp
added the qt UI project

@@ -1,0 +1,109 @@
+/****************************************************************************
+** Meta object code from reading C++ file 'mainwindow.h'
+**
+** Created by: The Qt Meta Object Compiler version 67 (Qt 5.2.1)
+**
+** WARNING! All changes made in this file will be lost!
+*****************************************************************************/
+
+#include "../mainwindow.h"
+#include <QtCore/qbytearray.h>
+#include <QtCore/qmetatype.h>
+#if !defined(Q_MOC_OUTPUT_REVISION)
+#error "The header file 'mainwindow.h' doesn't include <QObject>."
+#elif Q_MOC_OUTPUT_REVISION != 67
+#error "This file was generated using the moc from 5.2.1. It"
+#error "cannot be used with the include files from this version of Qt."
+#error "(The moc has changed too much.)"
+#endif
+
+QT_BEGIN_MOC_NAMESPACE
+struct qt_meta_stringdata_MainWindow_t {
+    QByteArrayData data[3];
+    char stringdata[35];
+};
+#define QT_MOC_LITERAL(idx, ofs, len) \
+    Q_STATIC_BYTE_ARRAY_DATA_HEADER_INITIALIZER_WITH_OFFSET(len, \
+    offsetof(qt_meta_stringdata_MainWindow_t, stringdata) + ofs \
+        - idx * sizeof(QByteArrayData) \
+    )
+static const qt_meta_stringdata_MainWindow_t qt_meta_stringdata_MainWindow = {
+    {
+QT_MOC_LITERAL(0, 0, 10),
+QT_MOC_LITERAL(1, 11, 21),
+QT_MOC_LITERAL(2, 33, 0)
+    },
+    "MainWindow\0on_pushButton_clicked\0\0"
+};
+#undef QT_MOC_LITERAL
+
+static const uint qt_meta_data_MainWindow[] = {
+
+ // content:
+       7,       // revision
+       0,       // classname
+       0,    0, // classinfo
+       1,   14, // methods
+       0,    0, // properties
+       0,    0, // enums/sets
+       0,    0, // constructors
+       0,       // flags
+       0,       // signalCount
+
+ // slots: name, argc, parameters, tag, flags
+       1,    0,   19,    2, 0x08,
+
+ // slots: parameters
+    QMetaType::Void,
+
+       0        // eod
+};
+
[…]

### 2014-04-16 UI/bin/ui_mainwindow.h

@@ -1,0 +1,122 @@
+/********************************************************************************
+** Form generated from reading UI file 'mainwindow.ui'
+**
+** Created by: Qt User Interface Compiler version 5.2.1
+**
+** WARNING! All changes made in this file will be lost when recompiling UI file!
+********************************************************************************/
+
+#ifndef UI_MAINWINDOW_H
+#define UI_MAINWINDOW_H
+
+#include <QtCore/QVariant>
+#include <QtWidgets/QAction>
+#include <QtWidgets/QApplication>
+#include <QtWidgets/QButtonGroup>
+#include <QtWidgets/QCheckBox>
+#include <QtWidgets/QHeaderView>
+#include <QtWidgets/QLabel>
+#include <QtWidgets/QLineEdit>
+#include <QtWidgets/QMainWindow>
+#include <QtWidgets/QMenuBar>
+#include <QtWidgets/QPushButton>
+#include <QtWidgets/QStatusBar>
+#include <QtWidgets/QToolBar>
+#include <QtWidgets/QWidget>
+
+QT_BEGIN_NAMESPACE
+
+class Ui_MainWindow
+{
+public:
+    QWidget *centralWidget;
+    QPushButton *pushButton;
+    QCheckBox *checkBox;
+    QCheckBox *checkBox_2;
+    QCheckBox *checkBox_3;
+    QCheckBox *checkBox_4;
+    QLineEdit *lineEdit;
+    QLineEdit *lineEdit_2;
+    QLabel *label;
+    QLabel *label_2;
+    QMenuBar *menuBar;
+    QToolBar *mainToolBar;
+    QStatusBar *statusBar;
+
+    void setupUi(QMainWindow *MainWindow)
+    {
+        if (MainWindow->objectName().isEmpty())
+            MainWindow->setObjectName(QStringLiteral("MainWindow"));
+        MainWindow->resize(560, 190);
+        centralWidget = new QWidget(MainWindow);
+        centralWidget->setObjectName(QStringLiteral("centralWidget"));
+        pushButton = new QPushButton(centralWidget);
+        pushButton->setObjectName(QStringLiteral("pushButton"));
+        pushButton->setGeometry(QRect(300, 90, 201, 32));
+        checkBox = new QCheckBox(centralWidget);
+        checkBox->setObjectName(QStringLiteral("checkBox"));
+        checkBox->setGeometry(QRect(30, 10, 101, 20));
+        checkBox->setChecked(false);
[…]

### 2014-04-16 UI/mainwindow.cpp

@@ -1,0 +1,24 @@
+#include "mainwindow.h"
+#include "ui_mainwindow.h"
+
+MainWindow::MainWindow(QWidget *parent) :
+    QMainWindow(parent),
+    ui(new Ui::MainWindow)
+{
+    ui->setupUi(this);
+}
+
+MainWindow::~MainWindow()
+{
+    delete ui;
+}
+
+void MainWindow::on_pushButton_clicked()
+{
+    char cmd[256];
+    sprintf(cmd,"source ~/graphcut_stereo/test.sh %s %s %s %s", ui->lineEdit->text().toStdString().c_str(),
+            ui->lineEdit_2->text().toStdString().c_str()
+            ,(ui->checkBox_4->checkState()==Qt::Checked)?"-swap":"-expansion",
+            (ui->checkBox->checkState()==Qt::Checked)?"-potts":"-linear");
+    system(cmd);
+}

### 2014-04-16 src/GraphcutStereo.cpp

@@ -13,6 +13,11 @@ GraphcutStereo::GraphcutStereo(int argc, char **argv)
     else
         alpha_beta_swap = false;
 
+    if(argc>4)
+        potts = (strcmp(argv[4],"-potts")==0?true:false);
+    else
+        potts = false;
+
     subpixel = false;
 
     drawHighRes = false;
@@ -227,6 +232,7 @@ void GraphcutStereo::glDraw()
 	    
 
             CVD::Rgb<CVD::byte> c = img0_4x4[i][j];
+            //CVD::Rgb<CVD::byte> c = img[0][i][j];
             glColor(c);
 //            float d = disparity4x4[i][j]; ;
 //            d = (d<=0)?1:d;
@@ -243,6 +249,12 @@ void GraphcutStereo::glDraw()
 
 void GraphcutStereo::Display()
 {
+    static bool saved = false;
+    if(saved)
+        return;
+    else
+        saved = true;
+
     Image<byte> disimg;
     disimg.resize(disparity.size());
 
@@ -258,6 +270,7 @@ void GraphcutStereo::Display()
 
     std::string output_name = fname;
     output_name.erase(output_name.begin()+output_name.length()-4,output_name.begin()+output_name.length());
+    output_name += (potts?"-potts-":"-linear-");
     if(alpha_beta_swap)
         CVD::img_save(disimg,output_name+ "disparity-swap.png");
     else
@@ -374,7 +387,7 @@ double GraphcutStereo::V(int i1, int j1, double dp1, int i2, int j2, double dp2)
     double val = 0;
     if(alpha_beta_swap)
     {
-        val = 100*fabs(dp1-dp2); //alpha beta swap
+        val = (potts?200:100)*fabs(dp1-dp2); //alpha beta swap
         if(val >= 100)
         {
             val = 100;
@@ -382,7 +395,7 @@ double GraphcutStereo::V(int i1, int j1, double dp1, int i2, int j2, double dp2)
     }
     else
     {
-        val = 5*fabs(dp1-dp2); //alpha expansion
+        val = (potts?100:5)*fabs(dp1-dp2); //alpha expansion
         if(val >= 50)
         {
             val = 50;
@@ -458,7 +471,8 @@ bool GraphcutStereo::AlphaBetaSwap(double f1, double f2)
     if(round > nF*nF*4)
     {
         Display();
-        exit(0);
+        //exit(0);
+        return true;
     }
 
     ImageRef size = image[0].size();
[…]

### 2014-04-16 src/GraphcutStereo.h

@@ -58,7 +58,7 @@ private:
 
     bool alpha_beta_swap;
     bool subpixel;
-
+    bool potts;
     //subsamplings
     CVD::Image<float> disparity4x4;
     CVD::Image<CVD::Rgb<CVD::byte> > img0_4x4;

### 2014-04-16 test.sh

@@ -1,0 +1,3 @@
+
+echo "testing..."
+~/graphcut_stereo/gstereo $1 $2 $3 $4
